Graph Testing

### 2019-08-02 notes/graph_testing.tex
updated weekly notes; began drafting master document

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}

@@

\makeatletter
\newcommand{\leqnomode}{\tagsleft@true}
\newcommand{\reqnomode}{\tagsleft@false}
\makeatother

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Var}[1]{\mathrm{Var}\left( #1 \right)}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\dotp}[2]{\langle #1 , #2 \rangle}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\defeq}{\overset{\mathrm{def}}{=}}
\newcommand{\convweak}{\overset{w}{\rightharpoonup}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\Bin}{\mathrm{Bin}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\text{vol}}
\newcommand{\Bal}{\textrm{Bal}}
\newcommand{\Cut}{\textrm{Cut}}
\newcommand{\Ind}{\textrm{Ind}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Perp}{\perp \! \! \! \perp}
\newcommand{\Naturals}{\mathbb{N}}

\newcommand{\Linv}{L^{\dagger}}
\newcommand{\tr}{\text{tr}}
\newcommand{\h}{\textbf{h}}
% \newcommand{\l}{\ell}
\newcommand{\x}{\textbf{x}}
\newcommand{\y}{\textbf{y}}
\newcommand{\bl}{\bm{\ell}}
\newcommand{\bnu}{\bm{\nu}}
\newcommand{\Lx}{\mathcal{L}_X}
\newcommand{\Ly}{\mathcal{L}_Y}
\DeclareMathOperator*{\argmin}{argmin}

\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\A}{\mathcal{A}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\N}{\mathbb{N}}
\newcommand{\E}{\mathcal{E}}

%%% Matrix related notation
\newcommand{\Xbf}{\mathbf{X}}
\newcommand{\Ybf}{\mathbf{Y}}
\newcommand{\Zbf}{\mathbf{Z}}
\newcommand{\Abf}{\mathbf{A}}
\newcommand{\Dbf}{\mathbf{D}}
\newcommand{\Wbf}{\mathbf{W}}
\newcommand{\Lbf}{\mathbf{L}}
\newcommand{\Ibf}{\mathbf{I}}
\newcommand{\Bbf}{\mathbf{B}}

%%% Vector related notation
\newcommand{\lbf}{\bm{\ell}}
\newcommand{\fbf}{\mathbf{f}}

%%% Set related notation
\newcommand{\Dset}{\mathcal{D}}
\newcommand{\Aset}{\mathcal{A}}
\newcommand{\Wset}{\mathcal{W}}

%%% Distribution related notation
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Qbb}{\mathbb{Q}}
% \newcommand{\Pr}{\mathrm{Pr}}}

%%% Functionals
\newcommand{\1}{\mathbf{1}}
\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden} 
\newtheorem{definition}{Definition}[section]

@@

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\begin{document}

\title{\textcolor{red}{Testing with Graphs}}
\author{Alden Green}
\date{\today}
\maketitle

\paragraph{Two-sample non-parametric hypothesis-testing problem.}

For fixed integers $n_1 + n_2 = n$, let $\Xbf = \set{x_1, \ldots, x_{n_1}} \subset \Rd$ and $\Ybf = \set{y_1, \ldots, y_{n_2}}$ be sampled i.i.d from distributions $\Pbb$ and $\Qbb$ with density functions $p$ and $q$, respectively, both with support on $D \subset \Rd$. Our statistical problem is testing the null hypothesis $H_0: \Pbb = \Qbb$ vs. the alternative $H_1: \Pbb \neq \Qbb$, where our knowledge of $\Pbb$ and $\Qbb$ come from the samples $\Xbf$ and $\Ybf$.

\paragraph{Integral Probability Metric.}
Given $\F$ a class of real-valued bounded measurable functions on $D$, the \emph{integral probability metric} between $\Pbb$ and $\Qbb$ with respect to $\F$ is
\begin{equation*}
\gamma_{\F}(\Pbb,\Qbb) = \sup_{f \in \F}\abs{\int_{D} f d\Pbb - \int_{D} f d\Qbb}
\end{equation*}

One such IPM that has not received close attention until surprisingly recently is the \emph{(weighted) Sobolev IPM}. For $f \in L^2(\Dset)$ and $\rho$ a density function over $\Dset$, the ($\rho^2$-weighted) Sobolev 1,2 norm of $f$ is given by
\begin{equation*}
\norm{f}_{1,2,\rho^2} := 
\begin{cases}
\int_{\Dset}\norm{\nabla_x f(x)}^2 \rho^2 dx,~ & \text{$f \in H^1(\Dset)$} \\
\infty,~ & \text{$f \in L^2(\Dset) \setminus H^1(\Dset)$}
\end{cases}
\end{equation*}
where $H^1(\Dset)$ is \textcolor{red}{the Sobolev space of $L^2(\Dset)$ functions with weak derivative $\nabla_x f(x) \in L^2(\Dset)$.}

Consider the unit ball of $\norm{\cdot}_{1,2,\rho^2}$,
\begin{equation*}
\Wset^{1,2}(\Dset,\rho^2) := \set{f: \norm{f}_{1,2,\rho^2} \leq 1}.
\end{equation*}
The weighted Sobolev IPM is simply $\gamma_{\Wset^{1,2}(\Dset,\rho^2)}(\Pbb,\Qbb)$.

\paragraph{Neighborhood graph.}

Let $G_{n,r_n} = (V,E,w)$ denote a weighted, undirected graph constructed from the samples $\Zbf = \set{z_1, \ldots, z_n} = (\Xbf,\Ybf)$ where $V = \set{1, \ldots, n}$, and $w_{uv} = K(z_u, z_v):= k(\frac{\norm{z_u - z_v}}{\epsilon_n}) \geq 0$ for $u,v \in V$, and a particular kernel function $k$. Here $(u,v) \in E$ if and only if $w_{uv} > 0$.

Motivated by the integral probability metric, our test statistics will be of the form
\begin{equation*}
\gamma_{\F_n}(\Pbb_n,\Qbb_n) = \sup_{f_n \in \F_n}\abs{\int_{D} f_n d\Pbb_n - \int_{D} f_n d\Qbb_n}
\end{equation*}
where
\begin{equation*}
\Pbb_n := \frac{1}{n_1}\sum_{i = 1}^{n_1} \delta_{x_i}, ~~ \Qbb_n := \frac{1}{n_2}\sum_{i = 1}^{n_2} \delta_{y_i}
\end{equation*}
are the empirical distributions of $\Xbf$ and $\Ybf$, respectively, and $\F_n$ is a \textcolor{red}{class of functions $f_n: \Zbf \to \Reals$ exhibiting some regularity with respect to the neighborhood graph $G_{n,r}$.}

\paragraph{Laplacian smoothing and Total Variation denoising.}

For convenience, we number the edges $E  = (e_1, \ldots, e_m)$. We denote by $\Bbf \in \Reals^{m \times n}$ the edge incidence matrix of $G_{n,r}$, which for $k$th edge $e_k = (u,v)$ has $k$th row $\Bbf_{k} = (0,\ldots,-w_{uv},\ldots,w_{uv},\ldots,0)$ with a $-w_{uv}$ in the $u$th location, and a $w_{uv}$ in the $v$th location. The random (unnormalized) Laplacian matrix is then $\Lbf = \Bbf^T \Bbf$. We also introduce a \emph{label vector}, given by $\lbf = (\ell_1, \ldots, \ell_n)$ with
\begin{equation}
\label{eqn: label_vector}
\ell_k = 
\begin{cases}
\frac{n}{n_1},~~~ \text{$z_k \in \Xbf$} \\
-\frac{n}{n_2}, ~ \text{$z_k \in \Ybf$}
\end{cases}
\end{equation}

Our test statistics $T_1(\lbf; G_{n,r})$ and $T_2(\lbf; G_{n,r})$ are defined as follows:
\begin{align*}
	T_1(\lbf; G_{n,r}) := \sup_{\fbf \in \Reals^n: \norm{\Bbf \fbf}_1 \leq C_{n,r}} ~ \frac{1}{n} \sum_{k = 1}^{n} \ell_k f_k \\
	T_2(\lbf; G_{n,r}) := \sup_{\fbf \in \Reals^n: \norm{\Bbf \fbf}_2^2 \leq C_{n,r}} ~ \frac{1}{n} \sum_{k = 1}^{n} \ell_k f_k
\end{align*}
where \textcolor{red}{$C_{n,r} = $} and we write $\fbf = (f_1,\ldots, f_n)$. We note that, as promised, these satisfy the form
\begin{align*}
T_1(\lbf; G_{n,r}) & = \sup_{f_n \in TV_n}\abs{\int_{D} f_n d\Pbb_n - \int_{D} f_n d\Qbb_n} \\
T_2(\lbf; G_{n,r}) & = \sup_{f_n \in \Wset_n}\abs{\int_{D} f_n d\Pbb_n - \int_{D} f_n d\Qbb_n}
\end{align*}
where $TV_n = \set{\fbf: \norm{\Bbf \fbf}_1 \leq C_{n,r}}$ and $\Wset_n = \set{\fbf: \norm{\Bbf \fbf}_2 \leq C_{n,r}}$.

\section{Consistency under fixed alternative}

\paragraph{Binomialized data model.}
For technical reasons, we would like $z_1, \ldots, z_n$ to be independent and identically distributed. We consider the following generative model, which we term the \emph{binomialized data model}:

Fix $n \in \Naturals > 0$, and $n_1 \sim \Bin(n,1/2),~ n_2 = n - n_1$. Then, let $x_1, \ldots, x_{n_1} \in \Rd$ be a sequence of i.i.d random points chosen according to $\Pbb$, and $y_1, \ldots, y_{n_2} \in \Rd$ a separate sequence of i.i.d random points chosen according to $\Qbb$, with $x_j \perp y_k$ for all $j,k$. Fix $\widetilde{\Zbf} = (\widetilde{z}_1,\ldots,\widetilde{z}_n) := (x_1, \ldots, x_{n_1}, y_1, \ldots, y_{n_2})$.  Finally, for a permutation $\pi: [n] \to [n]$ chosen uniformly at random among all such permutations, let $\Zbf = (z_1,\ldots,z_n) =  (\widetilde{z}_{\pi(1)}, \ldots, \widetilde{z}_{\pi(n)})$.

The label vector $\lbf$ remains defined as in \eqref{eqn: label_vector} with respect to $\Zbf$. Note that now $z_i \overset{i.i.d}{\sim} \frac{\Pbb}{2} + \frac{\Qbb}{2}$, as we desired, with density function $\mu(x) := \frac{p(x) + q(x)}{2}$.

\begin{theorem}
	\label{thm: LLN_for_t2}
	Let $d \geq 2$ and let $\Dset \subset \Rd$ be an open, bounded, connected set with Lipschitz boundary. Let $\mu$ satisfy
	\begin{equation*}
	m \leq \mu(x) \leq M \tag{$\forall x \in D$}
	\end{equation*}
	for some $0 < m \leq M$. Let $(r_n)$ be a sequence of positive numbers converging to $0$ and satisfying
	\begin{align*}
	& \lim_{n \to \infty} \frac{(\log n)^{3/4}}{n^{1/2}} \frac{1}{r_n} = 0 ~~ \text{if $d = 2$} \\
	& \lim_{n \to \infty} \frac{(\log n)^{1/d}}{n^{1/d}} \frac{1}{r_n} = 0 ~~ \text{if $d \geq 3$}
	\end{align*}
	Assume the kernel $k$ satisfies conditions: 
	\begin{align*}
	& k(0) > 0 ~ \text{and $k$ is continuous at $0$.} \tag{\textbf{K1}} \\
	& k~ \text{is non-increasing.} \tag{\textbf{K2}} \\
	& \text{The integral $\int_{0}^{\infty} k(r) r^{d+1} dr$ is finite.} \tag{\textbf{K3}}
	\end{align*}

	Then with probability one the following statement holds: For $(z_1, \ldots, z_n)$ chosen under the binomialized data model
	\begin{equation*}
	\lim_{n \to \infty} T_2(\lbf; G_{n,r_n}) = \gamma_{\Wset^{1,2}(\Dset,\mu^2)}(\Pbb,\Qbb).
	\end{equation*}
\end{theorem}

\section{Proofs}

Fix $\mu_n = \frac{d\Pbb_n + d\Qbb_n}{2}$. \textcolor{red}{We will show a variational form of convergence of $\mu_n$ to $\mu$.}

\subsection{Gamma convergence of constraint}

\begin{definition}[$TL^2$ convergence]
	Denote by $\mathfrak{B}(\Dset)$ the Borel $\sigma$-algebra of $\Dset$ and $\mathcal{P}(\Dset)$ the set of all Borel probability measures on $\Dset$. Given a Borel map $T: \Dset \to \Dset$, the \emph{push-forward} of $\mu$ by $T$ is given by
	\begin{equation*}
	T_{\star}\mu(\Aset) := \mu(T^{-1}(\Aset)), ~~ \Aset \in \mathfrak{B}(\Dset).
	\end{equation*}

	Given $\widetilde{\mu} \in \mathcal{P}(\Dset)$, we say that $T$ is a \emph{transportation map} between $\mu$ and $\widetilde{\mu}$ if $T_{\star}\mu = \widetilde{\mu}$. If for a sequence $(T_n)$ of transportation maps
	\begin{equation*}
	\int_{\Dset} \abs{x - T_n(x)}^2 d\mu(x) \to 0,~ \text{as $n \to \infty$}
	\end{equation*}
	we refer to the sequence as \emph{stagnating.}

	Take $f \in L^2(\mu)$ and a sequence $(f_n)$ with $f_n \in L^2(\mu_n)$ for $n = 1,2,\ldots$. If there exists a stagnating sequence of transportation maps $(T_n)$ such that
	\begin{equation*}
	\int_{\Dset} \abs{ f - T_n(f_n(x)) }^2 d\mu(x) \to 0,~ \text{as $n \to \infty$}
	\end{equation*}
	we say that $(f_n)$ converges $TL^2$ to $f$, and write $f_n \overset{TL^2}{\to} f$.
\end{definition}

We restate Theorem 1.4 of \cite{trillos2018}, changing notation to match the rest of this paper.

\begin{theorem}[Theorem 1.4 of \cite{trillos2018}]
	Under the setup and conditions of Theorem \ref{thm: LLN_for_t2}, with probability one the following statements hold:
	\begin{itemize}
		\item \emph{Liminf inequality:}
		For all $f \in L^2(\mu)$ and all sequences $(f_n)$ with $f_n \in L^2(\mu_n)$ and $f_n \overset{TL^2}{\to} f$,
		\begin{equation*}
		\liminf_{n \to \infty} \frac{1}{n^2 r_n^{d + 2}} \norm{Bf}_2^2 \geq \textcolor{red}{\sigma_{k}} \norm{f}_{1,2,\rho^2}
		\end{equation*}

		\item \emph{Limsup inequality:} For all $f \in L^2(\mu)$, there exists a sequence $(f_n)$ with $f_n \in L^2(\mu_n)$ and $f_n \overset{TL^2}{\to} f$ such that
		\begin{equation*}
		\limsup_{n \to \infty} \frac{1}{n^2 r_n^{d + 2}} \norm{Bf}_2^2 \leq \textcolor{red}{\sigma_{k}} \norm{f}_{1,2,\rho^2}
		\end{equation*}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{fullpage}
\usepackage{mathtools}

@@

\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\diam}{\mathrm{diam}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\text{vol}}
\newcommand{\spansp}{\mathrm{span}~}
\newcommand{\1}{\mathbf{1}}

\newcommand{\Linv}{L^{\dagger}}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

\newcommand{\emF}{\mathbb{F}_n}
\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\emP}{\mathbb{P}_n}
\newcommand{\F}{\mathcal{F}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Rd}{\Reals^d}

%%% Vectors
\newcommand{\thetast}{\theta^{\star}}

%%% Matrices
\newcommand{\X}{X} % no bold
\newcommand{\Y}{Y} % no bold
\newcommand{\Z}{Z} % no bold
\newcommand{\Lgrid}{L_{\grid}}
\newcommand{\Dgrid}{D_{\grid}}
\newcommand{\Linvgrid}{L_{\grid}^{\dagger}}

%%% Sets and classes
\newcommand{\Xset}{\mathcal{X}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Hclass}{\mathcal{H}}
\newcommand{\Pclass}{\mathcal{P}}

%%% Distributions and related quantities
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Ebb}{\mathbb{E}}
\newcommand{\Qbb}{\mathbb{Q}}

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\dif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\mathcal{D}}
\newcommand{\Hessian}{\mathcal{D}^2}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\dx}{\,dx}
\newcommand{\dy}{\,dy}
\newcommand{\dr}{\,dr}
\newcommand{\dxpr}{\,dx'}
\newcommand{\dypr}{\,dy'}
\newcommand{\wt}[1]{\widetilde{#1}}

%%% Order of magnitude
\newcommand{\soom}{\sim}

% \newcommand{\span}{\textrm{span}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden}

@@

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}

\begin{document}
\title{Graph Testing}
\author{Alden Green}
\date{\today}
\maketitle

\section{Fixed graph testing.}

Suppose we observe $G = (V,E)$, an undirected graph over $V = [n]$. Let $B$ be the $m \times n$ incidence matrix of $G$, with singular value decomposition $B = U\Lambda^{1/2}V^T$, so that the Laplacian matrix $L = V \Lambda V^T$. For $i \in [n]$, we observe
\begin{equation*}
z_i = \beta_i + \varepsilon_i, \quad \varepsilon_i \overset{\textrm{i.i.d}}{\sim} \mathcal{N}(0,1)
\end{equation*}
Our statistical goal is hypothesis testing. We wish to distinguish
\begin{equation*}
\mathbf{H}_0: \norm{\beta}_2 = 0 \quad \textrm{vs.} \quad \mathbf{H}_a: \norm{\beta}_2 > 0.
\end{equation*}
We will evaluate our performance using the notion of \emph{worst-case error}. For a given ``function'' class $\mathcal{H}$, test function $\phi: \Reals^n \to \set{0,1}$, and $\epsilon > 0$, let
\begin{equation*}
\mathcal{R}_{\epsilon}(\phi;\mathcal{H})= \Ebb_{0}(\phi) + \sup_{\beta \in \mathcal{H}:\norm{\beta}_2 > \epsilon} \Ebb_{\beta}(1 - \phi)
\end{equation*}

\subsection{Discrete Sobolev Classes.}

The first ``function'' class we will consider will be balls in discrete Sobolev norms, with known smoothness. For $s,d$ positive integers, and radius $C_n > 0$, let
\begin{equation*}
\mathcal{S}^{s}_{d}(C_n) = \set{\beta: \norm{D^{(s)}\beta}_2 \leq C_n}
\end{equation*}
where
\begin{equation*}
D^{(s)} = 
\begin{cases}
L^{s/2}, & \text{$s$ even} \\
DL^{(s-1)/2}, & \text{$s$ odd}.
\end{cases}
\end{equation*}
We note that the constraint is equivalent to $\beta^T V \Lambda^s V \beta \leq C_n^2$.
\subsection{Test statistic}
Let $0 = \lambda_0 \leq \lambda_1 \leq \lambda_2 \leq \ldots \leq \lambda_{n - 1}$ denote the ordered eigenvalues of $L$, and let $v_k$ denote the eigenvector corresponding to $\lambda_k$. For a constant $C > 0$ to be specified later, let 
\begin{equation*}
T_C = \sum_{k: \lambda_k^{s} \leq C^2} y_k^2
\end{equation*}
where
\begin{equation*}
y_k = \frac{1}{\sqrt{n}} \dotp{z}{v_k}.
\end{equation*}

We first compute the expectation $\Ebb(T_C)$. Let $\theta \in \Reals^n$ represent the expectation of $(y_k)$, meaning
\begin{equation*}
\theta_k = \frac{1}{\sqrt{n}}\dotp{\beta}{v_k}
\end{equation*}
and let $\Pi_C\theta$ have entries $(\Pi_C \theta)_k = \1(\lambda_k^{s} \leq C^2) \theta_k$. Finally, let $N(C) = \sharp\set{k: \lambda_k^{s} \leq C^2}$.

\begin{lemma}
	\label{lem:expectation}
	For any $\beta \in \Reals^n$,
	\begin{equation}
	\label{eqn:expectation_1}
	\Ebb(T_C) = \frac{N(C)}{n} + \norm{\Pi_C \theta}_2^2 
	\end{equation}
	If additionally $\beta \in \mathcal{H}$, the following lower bound holds:
	\begin{equation}
	\label{eqn:expectation_2}
	\Ebb(T_C) \geq \frac{N(C)}{n} + \frac{\norm{\beta}^2}{n}  - \frac{C_n^2}{nC^{2}}
	\end{equation}
\end{lemma}
\begin{proof}
	We can write
	\begin{align*}
	\Ebb(T_C) & = \sum_{k: \lambda_k^s \leq C} \Ebb(y_k^2) \\
	& = \frac{1}{n}\sum_{k: \lambda_k^s \leq C} \Ebb\bigl(\dotp{\beta}{v_k}^2 + \dotp{\varepsilon}{v_k}^2 + 2 \dotp{\varepsilon}{v_k} \dotp{\beta}{v_k}\bigr) \\
	& = \sum_{k: \lambda_k^s \leq C}\theta_k^2 + \frac{1}{n} \\
	& = \norm{\Pi_C \theta}^2 + \frac{N(C)}{n},
	\end{align*}
	showing \eqref{eqn:expectation_1}. Now, assuming, $\norm{D^{(s)}\beta}_2 \leq C_n$, we can further obtain
	\begin{align*}
	\norm{\Pi_C \theta}^2 & = \norm{\theta}^2 - \sum_{k:\lambda_k^s > C^2} \theta_k^2 \\
	& \geq \norm{\theta}^2 - \frac{1}{C^{2}}\sum_{k:\lambda_k^s > C^2} \theta_k^2 \lambda_k^s \\
	& \geq \norm{\theta}^2 -\frac{1}{nC^2} \beta^T V \Lambda^s V^T \beta \\
	& \geq \norm{\theta}^2  - \frac{C_n^2}{nC^{2}}
	\end{align*}
	and \eqref{eqn:expectation_2} is shown.
\end{proof}

We now turn to computing the variance $\Var(T_C)$.
\begin{lemma}
	\label{lem:variance}
	\begin{equation*}
	\Var(T_C) = \frac{2N(C)}{n^2} + \frac{4 \norm{\Pi_C \theta}_2^2}{n}
	\end{equation*}
\end{lemma}
\begin{proof}
	To begin, we rewrite
	\begin{align*}
	T_C & = \sum_{k:\lambda_k^s \leq C^2} y_k^2 \\
	& = \frac{1}{n} \sum_{k: \lambda_k^s \leq C^2} \dotp{z}{v_k}^2 \\
	& = \frac{1}{n} \sum_{k: \lambda_k^s \leq C^2} z^T v_k v_k^T z \\
	& =: \frac{1}{n} z^T P_{C} z.
	\end{align*}
	where $P_C := \sum_{k: \lambda_k^s \leq C^2} v_k v_k^T$. Therefore $\Var(T_C) = \Var(z^T P_{C} z)/n^2$. We expand $z = \beta + \varepsilon$ to obtain
	\begin{align}
	\Var(z^T P_{C} z) & = \Var((\beta + \epsilon)^T P_{C} (\beta + \epsilon)) \nonumber \\
	& = \Var(\beta^T P_{C} \beta + 2 \epsilon P_{C} \beta + \epsilon^T P_{C} \epsilon) \nonumber \\
	& = 4 \beta^T P_{C} I P_{C} \beta + \Var(\epsilon^T P_{C} \epsilon) + 4 \Cov(\epsilon P_{C} \beta, \epsilon^T P_{C} \epsilon) \nonumber \\
	& = 4 n \norm{\Pi_C \theta}_2^2 + \Var(\epsilon^T P_{C} \epsilon) \label{eqn:variance_1}
	\end{align}
	where the last equality follows from the Gaussianity of $\epsilon$, as
	\begin{equation*}
	\Ebb\bigl( (\epsilon P_{C} \beta) (\epsilon^T P_{C} \epsilon) \bigr) = \sum_{i = 1}^{n} \sum_{j = 1}^{n} \sum_{k = 1}^{n} (P_C\beta)_k (P_C)_{ij} \Ebb(\epsilon_i \epsilon_j \epsilon_k) = 0.
	\end{equation*}
	Also by the Gaussianity of $\epsilon$, $\epsilon^T P_C \epsilon \sim \chi_{N(C)}^2$, and therefore $\Var(\epsilon^T P_{C} \epsilon) = 2N(C)$. Plugging back into \eqref{eqn:variance_1}, we obtain
	\begin{equation*}
	\Var(z^T P_{C} z) = 4 n \norm{\Pi_C \theta}_2^2 + 2N(C) 
	\end{equation*}
	and therefore the desired result is proved.
\end{proof}

We will consider now the test $\phi_C = \mathbf{1}\{T(C) \geq N(C)/n + \tau(b)\}$, where for $b \geq 1$, $\tau(b) = b \sqrt{2N(C)/n^2}$. We first upper bound the type I error.

\begin{lemma}
	\label{lem:type_I_error}
	Under the null hypothesis $\beta = 0$, and for any $C > 0$,
	\begin{equation*}
	\Ebb_{\beta = 0}(\phi_C) \leq \frac{1}{b^2}. 
	\end{equation*}
\end{lemma}
\begin{proof}
	The desired result follows from Chebyshev's inequality,
	\begin{align*}
	\Ebb_{\beta = 0}(\phi) & = \Pbb_{\beta = 0}\bigl(T(C) \geq N(C)/n + \tau(b)\bigr) \\ 
	& = \Pbb_{\beta = 0}\bigl(T(C) - \frac{N(C)}{n} \geq \tau(b)\bigr) \\
	& \leq \Pbb_{\beta = 0}\bigl(\abs{T(C) - \frac{N(C)}{n}} \geq \tau(b)\bigr) \\
	& \leq \frac{\Var_{\beta = 0}(T_C)}{\tau(b)^2} = \frac{1}{b^2}.
	\end{align*}
\end{proof}
The calculation for the type II error will be slightly more involved.
\begin{lemma}
	\label{lem:type_II}
	Let $b \geq 1$ be fixed. For every $\beta \in \mathcal{S}_d^s(C_n)$ such that
	\begin{equation}
	\label{eqn:type_II}
	\frac{\norm{\beta}^2}{n} \geq 2b\sqrt{2\frac{N(C)}{n^2}} + \frac{C_n^2}{nC^2}
	\end{equation}
	we have that
	\begin{equation*}
	\Ebb_{\beta}(1 - \phi) \leq \frac{2}{b^2} + \frac{2}{b\sqrt{2N(C)}}.
	\end{equation*}
\end{lemma}
\begin{proof}
	Let $\Delta = \Ebb_{\beta}(T_C) - N(C)/n = \norm{\Pi_C \theta}^2$, and observe that by Lemma \ref{lem:expectation} and \eqref{eqn:type_II},
	\begin{equation*}
	\Delta \geq \frac{\norm{\beta}_2^2}{n} - \frac{C_n^2}{nC^2} \geq 2 \tau(b).
	\end{equation*}
	An application of Chebyshev's inequality yields
	\begin{align*}
	\Ebb_{\beta}\bigl(1 - \phi\bigr) & = \Pbb_{\beta}\bigl(T_C \leq N(C)/n + \tau(b)\bigr) \\
	& = \Pbb_{\beta}\bigl(T_C - \Ebb_{\beta}(T_C) \leq \tau(b) - \Delta \bigr) \\
	& \leq \Pbb_{\beta}\bigl(\abs{T_C - \Ebb_{\beta}(T_C)} \leq \Delta - \tau(b) \bigr) \tag{since $\Delta \geq \tau(b)$}	\\
	& \leq \frac{\Var_{\beta}(T_C)}{(\Delta - \tau(b))^2} \\
	& \leq 4\frac{\Var_{\beta}(T_C)}{\Delta^2} \tag{since $\Delta \geq 2\tau(b)$} \\
	& \leq 4\frac{2N(C)/n^2 + \norm{\Pi_C\theta}_2^2/n}{\Delta^2}.
	\end{align*}

	We now handle each summand separately. For the first term, since $\Delta \geq 2 \tau(b)$, we have
	\begin{equation*}
	\frac{2N(C)}{n^2\Delta^2} \leq \frac{1}{2b^2}.
	\end{equation*}

	For the second term, since $\Delta = \norm{\Pi_C\theta}^2$, we have
	\begin{align*}
	\frac{\norm{\Pi_C\theta}_2^2/n}{\Delta^2} & \leq \frac{1}{n\Delta^2} \\
	& \leq \frac{1}{2n\tau(b)} \\
	& = \frac{1}{2b\sqrt{2N(C)}}.
	\end{align*}
\end{proof}

To more explicitly specify the critical radius $\epsilon: \norm{\beta}_2 \geq \epsilon$, we will need to make an assumption on the relation between $N(C)$ and $C$. In particular, let $C = C^*$, where
\begin{equation*}
C^* = c\frac{(C_n n^{s/d})^{4s/(4s + d)}}{n^{s/d}}.
\end{equation*}
for some $c$ constant in $n$. We will assume the following bound on $N(C^*)$:
\begin{enumerate}[label=(A\arabic*)]
	\item Tail decay:
	\label{asmp:tail_decay}
	\begin{equation*}
	N(C^*) \leq (C^*)^{d/s}n
	\end{equation*}
\end{enumerate}
